---
title: "DDS_HW10_EDA_in_R"
author: "Jack K. Rasmus-Vorrath"
date: "July 20, 2017"
output: 
  html_document:
    keep_md: true
---

#The following EDA summarizes and visualizes factors of Click-Through-Rate data

##Q1: Data Import
```{r Question 1}
fileLocation <- "http://stat.columbia.edu/~rachel/datasets/nyt1.csv"
data1 <- read.csv(url(fileLocation))
head(data1)
```

##Q2: Age Grouping
```{r Question 2}
data1$Age_Group <- cut(data1$Age, c(-Inf, 18, 24, 34, 44, 54, 64, Inf))
levels(data1$Age_Group) <- c("<18", "18-24", "25-34", "35-44", "45-54", "55-64", "65+")
head(data1)
```

##Q3&4: Subset & Click-Through-Rate (CTR)
```{r Question 3&4}
d1 <-subset(data1, Impressions > 0)
d1$CTR <- d1$Clicks/d1$Impressions
head(d1)
```

##Q5: Impressions & CTR by Age_Group
```{r Question 5}
library(ggplot2)
ggplot(d1, aes(x = Impressions, fill = Age_Group)) + geom_histogram(binwidth = 1)
ggplot(subset(d1, CTR > 0), aes(x = CTR, fill = Age_Group)) + geom_histogram(binwidth = .025)
```

##Q6: CTR Grouping
```{r Question 6}
d1$CTR_Group <- cut(d1$CTR, c(-Inf, .2, .4, .6, .8, Inf))
levels(d1$CTR_Group) <- c("<.2", ".2-.4", ".4-.6", ".6-.8", ">.8")
head(d1)
```

##Q7: Summary Totals
```{r Question 7}
#Male = 1, Female = 0
g <- sum(d1$Gender)
g
sum(d1$Impressions)
sum(d1$Clicks)
s <- sum(d1$Signed_In)
s
```

##Q8: Means & Percents
```{r Question 8}
mean(d1$Age)
mean(d1$Impressions)
mean(d1$Clicks)
mean(d1$CTR)

#Percent Male
l_gender <- length(d1$Gender)
pct_male <- g/l_gender
pct_male

#Percent Signed_In
l_signedin <- length(d1$Signed_In)
pct_signedin <- s/l_signedin
pct_signedin
```

##Q9: Means & Percents by Age_Group
```{r Question 9}
#Means by Age_Group
library(doBy)
summary1 <- summaryBy(Impressions + Clicks + CTR ~ Age_Group, data = d1, FUN = mean)
summary1

#Percents by Age_Group
percent <- function(x){percent = sum(x)/length(x)}
summary2 <- summaryBy(Gender + Signed_In ~ Age_Group, data = d1, FUN = percent)
summary2
```

##Q10: Counts of CTR_Group & Age_Group
```{r Question 10}
library(plyr)
ctr_age <- count(d1, c('CTR_Group', 'Age_Group'))
ctr_age
```

##Q11&12: CTR_Group by Gender
```{r Question 11&12}
#All CTR_Groups
ggplot(d1, aes(x = CTR_Group, fill = factor(Gender)))+geom_bar()

#Excluding Lowest CTR_Group
ggplot(subset(d1, CTR_Group != "<.2"), 
       aes(x = CTR_Group, fill = factor(Gender)))+ geom_bar()

d2 <- subset(d1, CTR_Group != "<.2")
d3 <- subset(d2, CTR_Group != ".2-.4")
d4 <- subset(d3, CTR_Group != ".4-.6")

#Mid-to-High CTR_Groups by Gender
ggplot(d3, aes(x = CTR_Group, fill = factor(Gender)))+geom_bar()
ggplot(d4, aes(x = CTR_Group, fill = factor(Gender)))+geom_bar()

#Male-to-Female Ratio by CTR_Group
library(plyr)
ctr_gender <- count(d1, c('CTR_Group', 'Gender'))
m2f_CTR <- c(ctr_gender[2, 3]/ctr_gender[1, 3], ctr_gender[4, 3]/ctr_gender[3, 3], 
             ctr_gender[6, 3]/ctr_gender[5, 3], ctr_gender[8, 3]/ctr_gender[7, 3], 
             ctr_gender[10, 3]/ctr_gender[9, 3])
names(m2f_CTR) <- c("<.2", ".2-.4", ".4-.6", ".6-.8", ">.8")
m2f_CTR
```
##Consistently more Females than Males click through, especially in the middle-to-high CTR categories.